Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-08-12 doc/report/msc-report.tex
report: spelling correction.

As the name implies, MapReduce is made up of two parts or phases: map and
reduce. The user specifies a map function that consumes a single key/value pair
to generate a set of intermediate key/value pairs, and a reduce function that
merges all intermediate values that belongs to the same key. The abstraction of
two functions to process skmall parts of the large data set was inspired by the
map and reduce functions commonly found in functional programming languages such
as Lisp. The use of this model allows the framework to easily parallelize the
computations. In the inevitable case of a failure at a computational node, the
computations that failed can simply be re-executed on another node.

>>>>

As the name implies, MapReduce is made up of two parts or phases: map and
reduce. The user specifies a map function that consumes a single key/value pair
to generate a set of intermediate key/value pairs, and a reduce function that
merges all intermediate values that belongs to the same key. The abstraction of
two functions to process small parts of the large data set was inspired by the
map and reduce functions commonly found in functional programming languages such
as Lisp. The use of this model allows the framework to easily parallelize the
computations. In the inevitable case of a failure at a computational node, the
computations that failed can simply be re-executed on another node.
